The Strucplot Framework:\\ Visualizing Multi-way Contingency Tables with \pkg{vcd}

### 2005-11-02 trunk/vcd/paper/statreport22.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@495 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[notitle]{Z}

\usepackage{thumbpdf}
\usepackage{statreport}

\title{The Strucplot Framework:\\ Visualizing Multi-way Contingency
  Tables with \pkg{vcd}}

\author{
  \hfill David Meyer \hfill Achim Zeileis \hfill Kurt Hornik \hfill
  \\
  Wirtschaftsuniversit\"at Wien
  }

%\VignetteIndexEntry{The Strucplot Framework: Visualizing Multi-way Contingency Tables With package vcd}
%\VignetteDepends{vcd}
%\VignetteKeywords{contingency tables, mosaic plots, association plots, sieve plots, R, categorical data, independence, conditional independence, HSV, HCL, residual-based shading, grid}
%\VignettePackage{vcd}

%% need no \usepackage{Sweave.sty}

\SweaveOpts{engine=R,eps=TRUE,height=6,width=7,results=hide,fig=FALSE,echo=TRUE}
\setkeys{Gin}{width=0.7\textwidth}

\Plainauthor{David Meyer, Achim Zeileis, Kurt Hornik}

@@

\Keywords{contingency tables, mosaic plots, association plots, sieve plots, 
categorical data, independence, conditional independence, HSV, HCL,
residual-based shading, \texttt{grid}, \textsf{R}}

>>>>

\documentclass[notitle]{Z}
\usepackage{thumbpdf}
\usepackage{statreport}

%% need no \usepackage{Sweave}
\SweaveOpts{engine=R,eps=TRUE,height=6,width=7,results=hide,fig=FALSE,echo=TRUE}
\setkeys{Gin}{width=0.7\textwidth}

\title{The Strucplot Framework:\\ Visualizing Multi-way Contingency
  Tables with \pkg{vcd}}
\author{David Meyer \hspace{2cm} Achim Zeileis \hspace{2cm} Kurt Hornik\\
  Wirtschaftsuniversit\"at Wien}
\Plainauthor{David Meyer, Achim Zeileis, Kurt Hornik}
\Plaintitle{The Strucplot Framework: Visualizing Multi-way Contingency Tables with vcd}

@@

\Keywords{contingency tables, mosaic plots, association plots, sieve plots, 
categorical data, independence, conditional independence, HSV, HCL,
residual-based shading, \pkg{grid}, \textsf{R}}
\Plainkeywords{contingency tables, mosaic plots, association plots, sieve plots, 
categorical data, independence, conditional independence, HSV, HCL,
residual-based shading, grid, R}
